---
title: 
author: 
date: 
output:
  html_document:
    code_folding: hide
    df_print: paged
    toc: yes
    toc_depth: 6
    toc_float: 
      collapsed: false
---

<!--
Copyright 2020 Province of British Columbia

This work is licensed under the Creative Commons Attribution 4.0 International License.
To view a copy of this license, visit http://creativecommons.org/licenses/by/4.0/.
-->


```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)

library(readr)
library(janitor)
library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(here)
library(kableExtra)
library(safepaths) ## https://github.com/bcgov/safepaths

# results <- read_csv(use_network_path("7. Data Science CoP/surveys/results-survey424739 - final.csv"),
#                     col_types = c("cccccccccccccccccccccccccc")) %>%
#            clean_names()

results <- read_csv(here::here("surveys/tmp/survey_results.csv"))

participation <- results %>% count() %>% pull

```

# Data Science CoP March 2020 Survey Results

The Data Science CoP posted an online survey to gather community preferences and input for planning 2020 CoP activities. The survey was open for 3 weeks from March 4th to April 1st.

### Participation

 - `r  participation` community members completed the survey.

### Events

Support from survey participants varied in the types of events they would like to see the CoP host, however there was strongest support for continued training events and another data science demo day.

```{r}
events <- results %>% 
  select(starts_with("please")) %>% 
  pivot_longer(everything(), names_to = "question", values_to = "answer") %>% 
  mutate(question = str_remove(question, "please_select_events_from_the_list_below_that_you_would_you_like_to_see_the_data_science_co_p_host_in_2020_"), 
         question = recode(question, "co_p_member_led_data_science_learning_club_s" = "cop_member_led_data_science_learning_clubs"))


events %>% 
  filter(question != "other" & answer != "N/A") %>% 
  group_by(question, answer) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(labels = str_replace_all(question, "_", " "),
         labels2 = str_wrap(labels, 25)) %>% 
  ggplot(aes(answer, n)) +
  geom_col(fill = "#1f78b4", alpha = .7) +
  facet_wrap(~ labels2) +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank()) +
  labs(x = NULL, y = NULL)
```


Other event ideas suggested included:

```{r}

events %>% 
  filter(question == "other") %>% 
  drop_na() %>% 
  select(answer) %>% 
  mutate(answer = str_c("- ", answer)) %>% 
  pull() %>% 
  kable(col.names = NULL)
```


### Training

Support from survey participants was broadly similar for all the suggested training topics.

```{r}
what <- results %>% 
  select(starts_with("what_type_of")) %>% 
  pivot_longer(everything(), names_to = "question", values_to = "answer") %>% 
  mutate(question = str_remove(question, "what_type_of_training_event_you_would_like_to_see_the_data_science_co_p_host_in_2020_")) 


what %>% 
  filter(question != "other" & answer != "N/A") %>% 
  group_by(question, answer) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(labels = str_replace_all(question, "_", " "),
         labels2 = str_wrap(labels, 30)) %>% 
  ggplot(aes(answer, n)) +
  geom_col(fill = "#1f78b4", alpha = .7) +
  facet_wrap(vars(labels2)) +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank()) +
  labs(x = NULL, y = NULL)
```



Other suggested training topics included:

```{r}
what %>% 
  filter(question == "other") %>% 
  drop_na() %>% 
  select(answer) %>% 
  mutate(answer = str_c("- ", answer)) %>% 
  pull() %>% 
  kable(col.names = NULL)
```

### Computing Languages

So much in-house bcgov capacity in computer programming languages!

```{r}
results %>% 
  select(starts_with("what_programming_languages")) %>%
  rename("answer" = starts_with("what_programming_languages")) %>% 
  drop_na() %>%
  mutate(answer = str_c("- ", answer)) %>% 
  pull() %>% 
  kable(col.names = NULL)
```


### Other Suggested Topics

Many other great topics were suggested by survey participants:

```{r}
results %>% 
  select(starts_with("are_there_any_other_specific")) %>%
  rename("answer" = starts_with("are_there_any_other_specific")) %>% 
  drop_na() %>% 
  mutate(answer = str_c("- ", answer)) %>% 
  pull() %>% 
  kable(col.names = NULL)

```


### General Suggestions

Many, many great suggestions:

```{r}

results %>% 
  select(starts_with("do_you_have_any_additional_suggestions")) %>%
  rename("answer" = starts_with("do_you_have_any_additional_suggestions")) %>% 
  drop_na() %>% 
  mutate(answer = str_c("- ", answer)) %>% 
  pull() %>% 
  kable(col.names = NULL)
```
